---
title: "Report Network Analysis"
output:
  html_document:
    theme: united
    toc: TRUE
    number_sections: TRUE
    highlight: tango
    df_print: paged
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r}
#load("network_session.Rdata")
objs <- readRDS("network_session.rds")
attach(objs)
```
```{r}
library(qgraph)
library(d3heatmap)
library(purrr)
```

# Importante
As variáveis abaixo foram excluídas por terem níveis raros.
```{r}
data.frame("Variáveis_níveis_raros" = as.character(permutations_results$near_zero))
```

# Resultados

## Rede `r paste(desfecho, 0)`
```{r}
plot(netmeasures$net1)

node_names <- netmeasures$net1$graphAttributes$Nodes$names
data.frame("Número" = 1:length(node_names), node_names)

```

## Rede `r paste(desfecho, 1)`
```{r}

plot(netmeasures$net2)

node_names <- netmeasures$net2$graphAttributes$Nodes$names
data.frame("Número" = 1:length(node_names), node_names)

```

## Permutações

### Força global
A diferença na força global das redes dos conjuntos de dados reais foi de `r netmeasures$res$glstrinv.real` com valor p de `r netmeasures$res$glstrinv.pval`.    

```{r}
# glstrinv.real
# The difference in global strength between the networks of the observed (real) data sets.
# netmeasures$res$glstrinv.real

# glstrinv.pval
# The p value resulting from the permutation test concerning difference in global strength.
```

### Força global das redes  
```{r}
df_strength <- data.frame("Força_global" = netmeasures$res$glstrinv.sep)
rownames(df_strength) <- c("Network_1", "Network_2")
df_strength
```

```{r}
### glstrinv.perm
#The difference in global strength between the networks of the permutated data sets.
#hist(netmeasures$res$glstrinv.perm)
```

```{r}
### nwinv.real
# The value of the maximum difference M in any of the edge weights of the observed networks.
# netmeasures$res$nwinv.real

### nwinv.perm
#The values of the maximum difference in edge weights of the permuted networks.
#Não mostrado.
#nwinv.perm <- netmeasures$res$nwinv.perm

### nwinv.pval
#The p values resulting from the permutation test concerning the maximum difference in edge
#weights. When it=1000, there will be 1000 p values that form the reference distribution.
#netmeasures$res$nwinv.pval
```


### Valores das diferenças nos pesos dos conectores

```{r}
### einv.real
# The value of the difference in edge weight of the observed networks (multiple values if more
# edges are called to test).

einv.real <- netmeasures$res$einv.real
colnames(einv.real) <- colnames(data1)
rownames(einv.real) <- colnames(data1)
d3heatmap(einv.real, colors = "Oranges")
```


### Interações significativas
Apenas as interações com p corrigido por _Benjamini-Hochberg são mostradas abaixo.

```{r}
### einv.pvals
# TheBenjamini-Hochberg corrected p values per edge from the permutation test concerning differences in edges weights (if 0.00 = < 0.01)  

sig_int <-  netmeasures$res$einv.pvals[netmeasures$res$einv.pvals$`p-value` <= 0.05, ]
sig_int

#nrow(sig_int)/nrow(netmeasures$res$einv.pvals)*100


```

```{r}
### einv.perm
# The values of the difference in edge weight of the permuted networks. Only if test.edges =
# TRUE.  
# Não mostrado.
#netmeasures$res$einv.perm
```

# Mais informações
## Parâmetros 
### <code> mgm package </code>
*Levels*  
```{r}
vars_levels

```
k = 2  
lambdaSel = "CV"  
lambdaFolds = 10  
ruleReg = "AND"

### Parâmetros do code adaptado de NCT package
Numero de permutações: `r n_perm`.  
Seed:  `r seed`.  

## Dataset inicial inserido
```{r}
dt_merged
```

## Dimensões do dataset inicial
Número de linhas: `r nrow(dt_merged)`.  
Número de colunas (variáveis): `r ncol(dt_merged)`.  

## Frequência dos níveis das _features_
```{r}
map(dt_merged, table)
```

## Tipo das _features_
```{r}
vars_type <- as.factor(vars_type)
levels(vars_type) <- c("Categórica", "Gaussiana", "Poisson")
data.frame("Variáveis" = colnames(data1), "Tipo" = vars_type)
```

## _Datasets_ dividos pelo desfecho
```{r}
df <- rbind(dim(data1), dim(data2))
df <- as.data.frame(df)
colnames(df) <- c("Número de linhas", "Número de variáveis")
rownames(df) <- c("Dataset 1", "Dataset 2")
```

# Interações ordenadas pelo valor de p  
```{r}
netmeasures$res$einv.pvals[order(netmeasures$res$einv.pvals$`p-value`), ]
```
